### 2020-06-01 writeup/transfer.tex
intro

\begin{figure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.eps}
		\caption{Task similarity}
		\label{fig_model_shift}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.eps}
		\caption{Data size}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.eps}
		\caption{Covariate shift}
		\label{fig_covariate}
	\end{subfigure}
	\caption{Three takeaways of our theory in Section \ref{sec_insight}.
	(a) As task model distance increases, we observe a transition from positive to negative transfer  (Proposition \ref{prop_dist_transition}).
	(b) As source/target data ratio increases, we observe a transition from positive to negative transfer (Proposition \ref{prop_data_size}).
	(c) As covariate shift gets more severe (measured by increasing $\lambda$), MTL performance gets worse (Proposition \ref{prop_covariate}).
	The $y$-axis measures the performance of MTL minus STL.}
	\label{fig_model_shift_phasetrans}
\end{figure}

@@

@@

\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
Formally, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $x \cdot n_i$ datapoints from every task.
The data efficiency ratio is defined as
\[ \argmin_{x\in(0, 1)} ~~
		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
Using our tools, we show that in the isotropic model, the data efficiency ratio is
equal to \[ \frac{1}{\rho_1 + \rho_2} {+ \frac{1}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
The result can be also found in Appendix \ref{app_proof_32}.

@@

\begin{algorithm}[!t]
	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, W_2$ optimized for task $2$.
		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
				\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy after epoch $i$.
				\If{$a_i < a_{i-1}$ or $a_i > \tau$}
					\State \textbf{break}
				\EndIf
			\EndFor
		\EndFor
	\end{algorithmic}
\end{algorithm}

>>>>

@@

\begin{algorithm}[!t]
	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, W_2$ optimized for task $2$.
		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
			\EndFor
			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
				\State \textbf{break}
			\EndIf
		\EndFor
	\end{algorithmic}
\end{algorithm}

@@

\textbf{Connection to Taskonomy.} We use our tools to explain a key result of Taskonomy by Zamir et al.'18 \cite{ZSSGM18}, which shows that MTL can reduce the amount of labeled data needed to achieve comparable performance to STL.
Formally, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $x \cdot n_i$ datapoints from every task.
The data efficiency ratio is defined as
\[ \argmin_{x\in(0, 1)} ~~
		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
Using our tools, we show that in the isotropic model, the data efficiency ratio is
equal to \[ \frac{1}{\rho_1 + \rho_2} {+ \frac{1}{(\rho_1 +\rho_2)(\rho_1^{-1} + \rho_2^{-1} - \Theta(\Psi(\beta_1, \beta_2)))}}. \]
In addition to $\rho_1,\rho_2$, the data efficiency ratio also scales with $\Psi(\beta_1, \beta_2)$, the model distance between the tasks.
The result can be found in Appendix \ref{app_proof_32}.

@@
